Buildtime Trend : What's trending in your build process

### 2015-03-29 buildtimetrend/presentation.tex
update event title
small improvements
add slide about deploying to Heroku
format some things in italics

\date[NewLine 5Apr2015]{NewLine - Ghent\\

@@

      \item script to parse the generated timestamps

@@

      \item use this data to generate the chart

@@

@@

@@

@@

    Trigger the service at the end of a Travis CI build in .travis.yml :

>>>>

\date[NewLine 0x05 5Apr2015]{NewLine 0x05 - Ghent\\

@@

      \item parse the generated timestamps

@@

      \item generate the chart

@@

    \frametitle{First release - features}

@@

    <Add project schema>

@@

    \frametitle{Deploy to Heroku during Travis CI build}
    In \textit{.travis.yml} :
      \small{deploy:\\
      \ \ provider: heroku\\
      \ \ api\_key:\\
      \ \ \ \ secure: <secure key>\\
      \ \ app:\\
      \ \ \ \ deploy-prod: buildtimetrend}
    Branch \textit{deploy-prod} is deployed to app \href{https://buildtimetrend.herokuapp.com/}{https://buildtimetrend.herokuapp.com/}

@@

    Trigger the service at the end of a Travis CI build in \textit{.travis.yml} :
